### 2016-10-12 ARTICLES/RR_IJPP/evaluation.tex
Rapport de recherche avec contenu de la soumission IJPP

\paragraph{\textbf{Weak scaling}}
\begin{figure}[t]
\begin{minipage}{.475\textwidth}
  \includegraphics[width=\textwidth]{../results/weak_scaling/400/median_weak.pdf}
  \caption{weak-scaling with $400 \times 400$ domain per core.}
  \label{fig:weak1}
\end{minipage}
\hfill
\begin{minipage}{.475\textwidth}
  \includegraphics[width=\textwidth]{../results/weak_scaling/800/median_weak.pdf}
  \caption{weak-scaling with $800 \times 800$ domain per core.}
  \label{fig:weak2}
\end{minipage}\end{figure}
%In a weak scaling, a constant amount of work is given to each core while increasing the overall number of cores.
%As a result, the overall domain size also increase with the number of cores.
%A weak scaling is a good evaluation to detect overheads which are independent from the amount of computation performed by each core, such as collective communications, or overheads introduced by \llc components, for example.
Figures~\ref{fig:weak1} and~\ref{fig:weak2} show a weak scaling for a $400 \times 400$ points by core and a $800 \times 800$ points by core from 16 cores to 16.384 cores.
Minimum and maximum values are also shown as error bars in figures.

@@

\paragraph{\textbf{Strong scaling}}
\begin{figure}[t]\begin{center}
  \includegraphics[width=.6\textwidth]{../results/strong_scaling/10K_1K/median_strong.pdf}
  \caption{Strong scaling on a $10k \times 10k$ domain.}
  \label{fig:strong}
\end{center}\end{figure}
% The second evaluation is a strong scaling evaluation.
% Unlike a weak scaling, a strong scaling keeps a constant overall size of problem, while the number of cores increase.
% As a result, the sub-domain computed by each core reduces while the number of cores increases.
% The strong scaling is a good additional evaluation to the weak scaling, showing different kinds of overheads, such as cache misses (when the size of sub-domain becomes small enough to fit into cache memory), or small constant overheads.
Figure~\ref{fig:strong} shows the number of iteration per second for a 10k$\times$10k global domain size from 16 to 16.384 cores.
The ideal strong scaling is also illustrated.

@@

\begin{figure}[!h]\begin{center}
  \includegraphics[width=.6\textwidth]{../results/task_scaling/500_200/fusVSbase.pdf}
  \caption{Strong scaling on a 500x500 domain, with and without the fusion optimization.}
  \label{fig:fusion}
\end{center}\end{figure}

@@

\begin{figure}[bh]\begin{center}
  \includegraphics[width=.6\textwidth]{../results/task_scaling/500_200/analytic/times.pdf}
  \caption{Computation vs communication times in the data parallelization technique.}
  \label{fig:limit}
\end{center}\end{figure}

@@

\begin{figure}[th]\begin{center}
  \includegraphics[width=.6\textwidth]{../results/task_scaling/500_200/base_close_median.pdf}
  \caption{Strong scaling comparisons between data parallelization and hybrid parallelization. A \emph{close} OpenMP clause is used to bind threads onto cores.}
  \label{fig:close}
\end{center}\end{figure}

@@

\begin{figure}[!h]\begin{center}
  \resizebox{8cm}{!}{\includegraphics{../results/task_scaling/500_200/base_spread_median.pdf}}
  \caption{Strong scaling comparisons between data parallelization and hybrid parallelization. A \emph{spread} OpenMP clause is used to bind threads onto cores.}
  \label{fig:spread}
\end{center}\end{figure}

@@

\begin{figure}[!h]\begin{center}
  \resizebox{8cm}{!}{\includegraphics{../results/task_scaling/500_200/analytic/tth.pdf}}
  \caption{Execution times (seconds) of $T_{COM1}$ and $T_{COM2} + T_{task}$ for 8 cores for task parallelization. Verification of the Equation~(\ref{eq:hyb}).}
  \label{fig:tth2}
\end{center}\end{figure}

>>>>

\paragraph{\textbf{Weak scaling}}
\begin{figure}[t]
\begin{minipage}{.475\textwidth}
  \includegraphics[width=\textwidth]{../IJPP/results/weak_scaling/400/median_weak.pdf}
  \caption{weak-scaling with $400 \times 400$ domain per core.}
  \label{fig:weak1}
\end{minipage}
\hfill
\begin{minipage}{.475\textwidth}
  \includegraphics[width=\textwidth]{../IJPP/results/weak_scaling/800/median_weak.pdf}
  \caption{weak-scaling with $800 \times 800$ domain per core.}
  \label{fig:weak2}
\end{minipage}\end{figure}
%In a weak scaling, a constant amount of work is given to each core while increasing the overall number of cores.
%As a result, the overall domain size also increase with the number of cores.
%A weak scaling is a good evaluation to detect overheads which are independent from the amount of computation performed by each core, such as collective communications, or overheads introduced by \llc components, for example.
Figures~\ref{fig:weak1} and~\ref{fig:weak2} show a weak scaling for a $400 \times 400$ points by core and a $800 \times 800$ points by core from 16 cores to 16.384 cores.
Minimum and maximum values are also shown as error bars in figures.

@@

\paragraph{\textbf{Strong scaling}}
\begin{figure}[t]\begin{center}
  \includegraphics[width=.6\textwidth]{../IJPP/results/strong_scaling/10K_1K/median_strong.pdf}
  \caption{Strong scaling on a $10k \times 10k$ domain.}
  \label{fig:strong}
\end{center}\end{figure}
% The second evaluation is a strong scaling evaluation.
% Unlike a weak scaling, a strong scaling keeps a constant overall size of problem, while the number of cores increase.
% As a result, the sub-domain computed by each core reduces while the number of cores increases.
% The strong scaling is a good additional evaluation to the weak scaling, showing different kinds of overheads, such as cache misses (when the size of sub-domain becomes small enough to fit into cache memory), or small constant overheads.
Figure~\ref{fig:strong} shows the number of iteration per second for a 10k$\times$10k global domain size from 16 to 16.384 cores.
The ideal strong scaling is also illustrated.

@@

\begin{figure}[!h]\begin{center}
  \includegraphics[width=.6\textwidth]{../IJPP/results/task_scaling/500_200/fusVSbase.pdf}
  \caption{Strong scaling on a 500x500 domain, with and without the fusion optimization.}
  \label{fig:fusion}
\end{center}\end{figure}

@@

\begin{figure}[bh]\begin{center}
  \includegraphics[width=.6\textwidth]{../IJPP/results/task_scaling/500_200/analytic/times.pdf}
  \caption{Computation vs communication times in the data parallelization technique.}
  \label{fig:limit}
\end{center}\end{figure}

@@

\begin{figure}[th]\begin{center}
  \includegraphics[width=.6\textwidth]{../IJPP/results/task_scaling/500_200/base_close_median.pdf}
  \caption{Strong scaling comparisons between data parallelization and hybrid parallelization. A \emph{close} OpenMP clause is used to bind threads onto cores.}
  \label{fig:close}
\end{center}\end{figure}

@@

\begin{figure}[!h]\begin{center}
  \resizebox{8cm}{!}{\includegraphics{../IJPP/results/task_scaling/500_200/base_spread_median.pdf}}
  \caption{Strong scaling comparisons between data parallelization and hybrid parallelization. A \emph{spread} OpenMP clause is used to bind threads onto cores.}
  \label{fig:spread}
\end{center}\end{figure}

@@

\begin{figure}[!h]\begin{center}
  \resizebox{8cm}{!}{\includegraphics{../IJPP/results/task_scaling/500_200/analytic/tth.pdf}}
  \caption{Execution times (seconds) of $T_{COM1}$ and $T_{COM2} + T_{task}$ for 8 cores for task parallelization. Verification of the Equation~(\ref{eq:hyb}).}
  \label{fig:tth2}
\end{center}\end{figure}
